Group A

### 2023-08-24 group-a/E1-analysis-calibration-Hartshorne.Rmd

---
title: "E1 JH data calibration"
author: "Ariel James"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r}
#To be run after E1-analysis-replication.Rmd
#Correlates subjects' experimental effects with their calibration quality (from df called "validation.percent").
```
<!-- # Setup -->
```{r E1-c-JH-setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(readr)
library(afex)
library(forcats)
library(papaja)
source("~/round.comm.R")

>>>>

---
title: "E1 JH data calibration"
author: "Ariel James"
date: "`r Sys.Date()`"
output: pdf_document
---
<!-- NO LONGER USED! CRAMMED EVERYTHING INTO E1-ANALYSIS-COMPARISON-TO-HARTSHORNE-->
```{r}
#To be run after E1-analysis-replication.Rmd
#Correlates subjects' experimental effects with their calibration quality (from df called "validation.percent").
```
<!-- # Setup -->
```{r E1-c-JH-setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(readr)
library(afex)
library(forcats)
library(papaja)
source("~/round.comm.R")

### 2023-08-24 group-a/E1-analysis-calibration.Rmd

```{r}
#To be run after E1-analysis-replication.Rmd
#Correlates subjects' experimental effects with their calibration quality (from df called "validation.percent").
```
<!-- # Setup -->
```{r E1-c-setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(readr)
library(afex)
library(forcats)
library(papaja)
source("~/round.comm.R")

>>>>

```{r}
#To be run after E1-analysis-replication.Rmd
#Correlates subjects' experimental effects with their calibration quality (from df called "validation.percent").
```
<!-- # Setup -->
```{r E1-c-setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(readr)
library(afex)
library(forcats)
library(papaja)
source('round.comm.R')

### 2023-08-24 group-a/E1-analysis-comparison-to-Hartshorne.Rmd

---
title: "Group A, in-lab"
output: pdf_document
---
<!-- # Setup -->
```{r E1-JH-setup, include = FALSE, echo = FALSE}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(readr)
library(afex)
library(forcats)
library(papaja)
library(patchwork)
source("~/round.comm.R")

>>>>

---
title: "Group A, in-lab"
output: pdf_document
---
<!-- # Setup -->
```{r E1-JH-setup, include = FALSE, echo = FALSE}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(readr)
library(afex)
library(forcats)
library(papaja)
library(patchwork)
source('round.comm.R')

### 2023-08-24 group-a/E1-analysis-comparison-to-JMW23.Rmd

```{r import JMW23}
JMW1_info <- read_csv("group-a/JMW23-data/fyptrialinfo.csv")
JMW1_data <- read.delim("group-a/JMW23-data/FYPTimecourse_by_subj.txt", header = FALSE, sep = ",")
#Add meaningful header row
tc_header = c("TARGET","AGENT", "COMP1", "COMP2", "COMP3", 
              "NON1", "NON2", "NON3", "NON4", "NON5",
              "ORDER", "SUBJ", "BIN", "COND", "AID") #AID is a unique item number

@@

#AJ: this is where you left off. Everything above should work :)
JMW_spag_fig <- ggplot(JMW_cumu.summary, aes(x=t.window, y=cumulative.fixation.m, fill=obj_class, shape=COND, group=interaction(COND, obj_class)))+
  scale_fill_manual(values=c("white", "black"))+
  scale_shape_manual(values=c(22,21))+
  geom_line()+
  geom_point(size=2)+
  theme_bw()+
  theme(panel.grid=element_blank())+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type") +
  geom_vline(xintercept = mean(JMW1_info$Non.relative))

JMW_spag_fig

#The "Object type" part of the key doesn't actually show which color is which
```

>>>>

```{r import JMW23}
JMW1_info <- read_csv("group-a/JMW23-data/fyptrialinfo.csv")

JMW1_latency <- read.delim("group-a/JMW23-data/FYPAKFixationLatenciesPOSTVERB.txt", header = FALSE, sep = ",") #I'll come back to this

JMW1_data <- read.delim("group-a/JMW23-data/FYPTimecourse_by_subj.txt", header = FALSE, sep = ",")

#Add meaningful header row
tc_header = c("TARGET","AGENT", "COMP1", "COMP2", "COMP3", 
              "NON1", "NON2", "NON3", "NON4", "NON5",
              "ORDER", "SUBJ", "BIN", "COND", "AID") #AID is a unique item number

@@

#AJ: this is where you left off. Everything above should work :)
JMW_spag_fig <- ggplot(JMW_cumu.summary, aes(x=t.window, y=cumulative.fixation.m, fill=obj_class, shape=COND, group=interaction(COND, obj_class)))+
  scale_fill_manual(values=c("white", "black"))+
  scale_shape_manual(values=c(22,21))+
  geom_line()+
  geom_point(size=2)+
  theme_bw()+
  theme(panel.grid=element_blank())+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type") +
  geom_vline(xintercept = mean(JMW1_info$Non.relative))
#The "Object type" part of the key doesn't actually show which color is which
```

### 2023-08-24 group-a/E1-analysis-replication.Rmd

---
title: "Group A"
output: pdf_document
---
<!-- # Setup -->
```{r E1-setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(readr)
library(afex)
library(forcats)
library(papaja)
source("~/round.comm.R")

@@

*TO-DO: Confirm: what was done with fixations initiated prior to verb onset that persisted past verb onset (I think I should be able to tell from looking at the code) whether there's a 200-ms scootch.

@@

E1_model2_tab.min = broom.mixed::tidy(E1_model2.min) 
E1_model2_obj.min = E1_model2_tab.min %>% filter(term == "object_classtarget.object")
E1_model2_verb.min = E1_model2_tab.min %>% filter(term == "verb_typerestricting")
E1_model2_obj_verb.min = E1_model2_tab.min %>% filter(term == "object_classtarget.object:verb_typerestricting")
```
#### Pre-verb-offset fixations
Altmann & Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above. When we do the same, we again see that the critical interaction is not significant but numerically in the expected direction (_b_ = `r E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).

@@

```{r}
first.fixation.after.verb.onset.min <- critical.trials.filtered.min %>%
  group_by(subject_id, image_name) %>%
  filter(t >= verb_onset*1000) %>%
  filter(object_type == "target.object") %>%
  filter(is.fixating == TRUE) %>%
  filter(t == min(t)) %>%
  mutate(noun_relative.t = t - (postverbal_noun_onset*1000)) %>%
  mutate(von_relative.t = t - (verb_onset*1000)) %>%
  mutate(voff_relative.t = t - (verb_offset*1000)) %>%
  mutate(det_relative.t = t -(postverbal_determiner_onset*1000))
```

@@

```
#### First target fixations after verb
Finally, we address whether participants look to the target faster in the restrictive vs. the non-restrictive condition, starting after the onset of the verb. [TO-DO: On average, participants looked to the target X ms after (AK's Table 1)..., I'll also want to say the lengths of the verbs. AK's Table 2] We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes. There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (_b_ = `r E1_model3_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.min %>% pull(p.value) %>% round(digits = 2)`).

>>>>

---
title: "Group A"
output: pdf_document
---
<!-- # Setup -->
```{r E1-setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(readr)
library(afex)
library(forcats)
library(papaja)
source('round.comm.R') #does "commercial" i.e. normal rounding

@@

<!--Confirm: what was done with fixations initiated prior to verb onset that persisted past verb onset;  whether there's a 200-ms scootch. Answer: fixations beginning at or before verb onset are not included in cumulative fixation data or first fixation data. There is no 200-ms scootch.-->

@@

E1_model2_tab.min = broom.mixed::tidy(E1_model2.min) 
E1_model2_obj.min = E1_model2_tab.min %>% filter(term == "object_classtarget.object")
E1_model2_verb.min = E1_model2_tab.min %>% filter(term == "verb_typerestricting")
E1_model2_obj_verb.min = E1_model2_tab.min %>% filter(term == "object_classtarget.object:verb_typerestricting")
```
#### Pre-verb-offset fixations
Altmann and Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above. When we do the same, we again see that the critical interaction is not significant but numerically in the expected direction (_b_ = `r E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).

@@

```{r}
first.fixation.after.verb.onset.min <- critical.trials.filtered.min %>%
  group_by(subject_id, image_name) %>%
  filter(t >= verb_onset*1000) %>% #excludes fixations initiating on or before verb
  filter(object_type == "target.object") %>%
  filter(is.fixating == TRUE) %>%
  filter(t == min(t)) %>% #earliest fixation
  mutate(noun_relative.t = t - (postverbal_noun_onset*1000)) %>%
  mutate(von_relative.t = t - (verb_onset*1000)) %>%
  mutate(voff_relative.t = t - (verb_offset*1000)) %>%
  mutate(det_relative.t = t -(postverbal_determiner_onset*1000))
```

@@

```
#### First target fixations after verb
Finally, we address whether participants look to the target faster in the restrictive vs. the non-restrictive condition, starting after the onset of the verb. [TO-DO: On average, participants looked to the target `r E1_latency_table_min$Eat.x[2]` ms after the noun onset in the restrictive condition (compared to ) and `r E1_latency_table_min$Eat.x[2]` ms after the noun onset in the non-restrictive condition (compared to )]. Thus, first fixations were not only delayed relative to those in the previous studies compared here, but also showed a smaller difference between conditions.

We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes. There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (_b_ = `r E1_model3_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.min %>% pull(p.value) %>% round(digits = 2)`).
